point.distance

### 2022-04-13 src/data.prep.Rmd
update

library(data.table)
library(tidyverse)
library(rprojroot)

@@

The internet archive data is saved on /hdd

@@

all <- fread(data.path)
#glimpse(all)
unique(all$year)

all$id <- seq.int(nrow(all))

# for test at the end
test.all <- dim(all[1])

@@

Postcode lookup.

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- fread(path.lookup)
#glimpse(lookup)
```
Merge

```{r}
setkey(lookup, pcds)
setkey(all, pc)
all.msoa <- lookup[all]

sapply(all.msoa, function(x) sum(is.na(x)))
```

The next snippet drops URLS from the same host referring to same postcode, which
were observed more than once per year. 
In other words, it drops URLs, which were archived multiple times per year.

```{r}
all.msoa <- unique(all.msoa, by = c("host", "year", "pcds"))
```

Aggregate

```{r}
msoa <- all.msoa[, .(count.url=.N), by = .(year, msoa11cd)]
```

@@

Drop the observations without MSOA code

```{r}
msoa <- msoa[!is.na(msoa11cd)]
```

Export

```{r}
path.out <- paste0(path, "/data/temp/msoa.csv")
fwrite(msoa, path.out) # for all obs
```

>>>>

library(tidyverse)
library(rprojroot)

@@

The internet archive data is saved on /hdd.
Split to yearly files.

@@

read_csv(data.path) %>% 
  #distinct(host, year)
  group_by(year) %>%
  #group_walk(~ write_csv(.x, paste0(.y$year, ".csv"))) #
  group_map(~ write_csv(.x, paste0(path,"/data/temp/msoa", .y$year, ".csv")))
```
Postcode lookup.

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  select(pcds, msoa11cd) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd
```

Bring MSOA code and then aggregate per MSOA.

```{r}

# all <- read_csv(data.path)
# all %>% 
#   #mutate(id = 1:n()) %>% #seq.int(nrow())) %>% 
#   #mutate(id = id(.)) %>% 
#   left_join(lookup, by = "pc", suffix =c("","")) %>% 
#   distinct(host, year, pc, .keep_all = TRUE) %>% 
#   group_by(msoa11cd) %>% 
#   summarise(count.url=sum(N))
#   write_csv(paste0(path,"/data/temp/data", "X", ".csv"))

files <- list.files(path=paste0(path,"/data/temp"), pattern="*.csv", full.names=TRUE, recursive=FALSE)
lapply(files, function(x) {
  read_csv(x, col_names = T) %>% 
    #mutate(id = id(.)) %>%  
    left_join(lookup, by = "pc", suffix =c("","")) %>%

    # strips out the timestamp from the url
    mutate(url.no.date = substring(url, 16)) %>%

    # OLD
    # Drops URLS from the same host referring to same postcode, which
    # are observed more than once per year. 
    # In other words, it drops URLs, which were archived multiple times per year.
    #distinct(host, pc,  .keep_all = TRUE) %>%

    # Drops URLs (no timestamp) referring to same postcode, which
    # are observed more than once per year. 
    # In other words, it drops pairs of URLs and postcodes, which were archived multiple times per year.
    distinct(url.no.date, pc, .keep_all = TRUE) %>%

    # OLD Aggregate
    #group_by(msoa11cd) %>% 
    #summarise(count.url=sum(N)) %>%

    # Aggregate:
    # Counts how many unique pairs of url.no.date and pc exist in every MSOA per year.
    # In other words, it provides the number of georeferenced archived webpages per MSOA and year
    count(msoa11cd) %>%

    write_csv(x)
})

# for test at the end
#test.all <- dim(all[1])

@@

@@

### 2022-04-13 src/hex_heatmaps.Rmd
update

---
title: "hdbscan"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

library(tidyverse)
library(rprojroot)
library(rgdal)
library(spdep)
library(dbscan)

@@

## hdbscan

```{r}
t = 1998

x <- df %>%
    #slice_sample(n = 10000) %>% 
    filter(!is.na(oseast1m), #6k rows with missing east/north for all years
           year == t,
           substr(pc, 1,2) !="BT") %>% #drop Northern Ireland, for 2010 c. 4k obs.
    st_as_sf(coords = c("oseast1m", "osnrth1m"), crs = 27700) %>%
    st_transform(4326) %>%
    st_coordinates() %>%
    as_tibble()

kNNdistplot(x, k = 2)               # it runs on the console
abline(h=.3, col = "red", lty=2)

res <- dbscan(x, eps = 0.1, minPts = 3)

plot(x, col = res$cluster + 1L, pch = res$cluster + 1L)
hullplot(x, res)

res <- optics(x, eps = 10, minPts = 10)
```

>>>>

---
title: "diffusion, websites with 1 pc"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

library(tidyverse)
library(rprojroot)
library(rgdal)
library(spdep)
library(tmap)

@@

### 2022-04-13 src/level_lisa.Rmd
update

@@

df <- read_csv(data.path) %>% 
  filter(V1.domain == n,
         year > 1995) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, msoa11cd) %>%
  summarise(n = sum(V1.domain)) %>% 
  group_by(msoa11cd) %>%                   # turn on for growth
  mutate(growth = (n - lag(n))/lag(n)) %>% # turn on for growth 
  filter(year != 1996 )
```

@@

```{r, eval=F}
maps <- msoa
maps.df <- fortify(maps, region = "MSOA11CD")

base <- maps.df %>% left_join(df[df$year==t,], by = c("id"="msoa11cd")) %>% 
  # mutate(n = ifelse(is.na(n), 0, n),
  #        year = ifelse(is.na(year), 1996, year))
  ggplot(mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed() + 
  geom_polygon(color = NA, fill = "white")

ditch_the_axes <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank()
)

#N.web
base + 
  geom_polygon(aes(fill = growth), color = NA) +
  theme_bw() +
  ditch_the_axes + ggtitle(t) +
  theme(legend.title=element_text(size=5), legend.text=element_text(size=4)) +
  guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
  scale_fill_gradient2(midpoint = 0, mid="#eee8d5", high="#dc322f", low="#268bd2")

  scale_fill_gradientn(colours=c('light gray','dark blue'),
                     name='N. of web pages',na.value=NA)#, trans = "log10") #  breaks = c(100, 1000, 10000)
  #coord_map(xlim = c(200000, 300000),ylim = c(200000, 300000)) # zoom in

#ggsave("C:/net27/COSMIC/archive/gis/msoa_Nweb2001.png", dpi = 300, width=4, height=4)

@@

path.out <- paste0(path, "/outputs/lisa_growth_msoa")

for (t in 1997:2010){
test <- msoa
test@data <- test@data %>% left_join(df[df$year==t,], by = c("MSOA11CD"="msoa11cd")) #%>% 
  # mutate(n = ifelse(is.na(n), 0, n),
  #        year = ifelse(is.na(year), 1996, year))

@@

#Moran's I
globalMoran <- moran.test(test$growth, listw, zero.policy = T, na.action = na.exclude)
globalMoran

#LISA
lmoran<- cbind(test@data, localmoran(test$growth, listw,  adjust.x=TRUE, zero.policy = T, na.action = na.exclude))
#lmoran

# centers the local Moran's around the mean
lmoran$Ii <- lmoran$Ii - mean(lmoran$Ii, na.rm = TRUE) 
lmoran$lag.growth <- lag.listw(listw,lmoran$growth, NAOK = TRUE)

@@

lmoran$ns <- lmoran$growth - mean(lmoran$growth, na.rm = TRUE) 
lmoran$lag.growth <- lmoran$lag.growth - mean(lmoran$lag.growth, na.rm = TRUE)

@@

lmoran <- lmoran%>% 
  mutate(quadrant= ifelse(ns>0 & lag.growth > 0, 1, 0)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.growth < 0, 2, quadrant)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.growth > 0, 3, quadrant)) %>% 
  mutate(quadrant= ifelse(ns>0 & lag.growth < 0, 4, quadrant)) %>%   
  #mutate(quadrant= ifelse(lmoran$`Pr(z > 0)` > signif, 0, quadrant)) #%>% 
  mutate(quadrant= ifelse(lmoran$`Pr(z != E(Ii))` > signif, 0, quadrant)) #%>%

@@

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, palette=  c("white","red","blue",rgb(0,0,1,alpha=0.4),rgb(1,0,0,alpha=0.4)), labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), title="LISA for growth, MSOA") +
  tm_legend(text.size = 1) +
 # tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  # tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
    tm_borders(alpha=.5) +
   tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))

>>>>

Replace `msoa11cd1` with `oa11cd` for OA.

@@

df <- read_csv(data.path) %>% 
  filter(V1.domain == n,
         year > 1995) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, msoa11cd) %>%
  summarise(n = sum(V1.domain)) 
```

@@

@@

path.out <- paste0(path, "/outputs/lisa_n_msoa")

for (t in 1996:2010){
test <- msoa
test@data <- test@data %>% left_join(df[df$year==t,], by = c("MSOA11CD"="msoa11cd")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         year = ifelse(is.na(year), t, year))

@@

#Moran's I
globalMoran <- moran.test(test$n, listw, zero.policy = T, na.action = na.exclude)
globalMoran

#LISA
lmoran<- cbind(test@data, localmoran(test$n, listw,  adjust.x=TRUE, zero.policy = T, na.action = na.exclude))
#lmoran

# centers the local Moran's around the mean
lmoran$Ii <- lmoran$Ii - mean(lmoran$Ii, na.rm = TRUE) 
lmoran$lag.n<-  lag.listw(listw,lmoran$n, NAOK = TRUE)

@@

lmoran$ns <- lmoran$n - mean(lmoran$n, na.rm = TRUE) 
lmoran$lag.n <- lmoran$lag.n - mean(lmoran$lag.n, na.rm = TRUE)

@@

lmoran <- lmoran%>% 
  mutate(quadrant= ifelse(ns>0 & lag.n > 0, 1, 0)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.n < 0, 2, quadrant)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.n > 0, 3, quadrant)) %>% 
  mutate(quadrant= ifelse(ns>0 & lag.n < 0, 4, quadrant)) %>%   
  #mutate(quadrant= ifelse(lmoran$`Pr(z > 0)` > signif, 0, quadrant)) #%>% 
  mutate(quadrant= ifelse(lmoran$`Pr(z != E(Ii))` > signif, 0, quadrant)) #%>%

@@

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, palette=  c("white","red","blue",rgb(0,0,1,alpha=0.4),rgb(1,0,0,alpha=0.4)), labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), title="LISA for level, MSOA") +
  tm_legend(text.size = 1) +
 # tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  # tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
    tm_borders(alpha=.5) +
   tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))

### 2022-04-13 src/point_distance.Rmd
update

---
title: "diffusion, websites with 1 pc"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)

@@

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  select(pcds, oa11cd) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd
```

The internet archive $1996$-$2010$ data is saved on /hdd.
The internet archive $2011$-$2012$ data is saved on ~/projects/web.diffusion/data/temp.

```{r}
n = 1 #number of unique postcodes. 
m = 12

data.folder <- "/hdd/internet_archive/archive/data/"
data.path9610 <- paste0(data.folder, "domain_pc_year.csv")
#Created by domain.R, which uses domain instead of host.
#This is what we use for the hyperlinks paper as per George's script

df9610 <- read_csv(data.path9610)

data.path2011_2012 <- paste0(path, "/data/temp/domain_pc_year1112.csv")
#Created by domain1112.Rmd, which is based on domain.R and uses domain instead of host.
#This is what we use for the hyperlinks paper as per George's script

df1112 <- read_csv(data.path2011_2012)

df <- bind_rows(df9610, df1112) %>% 
  filter(
    V1.domain < m,             # for multiple pc
    #V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%            # for multiple pc  
  #summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

# tests for Scotland
# df %>% filter(substr(oa11cd, 1,1) =="S",
#               year==2010) %>% summarise(mean(n, na.rm = T))
# 
# df %>% filter(oa11cd=="S00090182")
# 
# test@data %>% filter(substr(id, 1,1) =="S",
#                      n!=0)
# 
# df %>% filter(substr(oa11cd, 1,1) =="W",
#               year==2003)
```

## spatial data

```{r}
# get OA for England and Wales
path.geo <- paste0(path, "/data/raw/Output_Areas__December_2011__Boundaries_EW_BGC.geojson")
oa.ew <- readOGR(path.geo)
# source: https://geoportal.statistics.gov.uk/

@@

# # get OA for Scotland
# path.geo.sc <- paste0(path, "/data/raw/SG_DataZoneBdry_2011")
# oa.sc <- readOGR(dsn=path.geo.sc, layer = "SG_DataZone_Bdry_2011")
# # source: https://data.gov.uk/dataset/ab9f1f20-3b7f-4efa-9bd2-239acf63b540/data-zone-boundaries-2011
# 
# # spatial transformations
# oa.sc <- spTransform(oa.sc, CRS("+init=epsg:4326"))
# 
# # Scotland (follows same steps as EW, see notes above)
# oa.sc <- oa.sc[, 'DataZone']
# colnames(oa.sc@data) <- c('id')
# 
# # reassign the polygon IDs
# oa.sc <- spChFIDs(oa.sc, as.character(oa.sc$id))
# 
# # check the CRS has changed correctly, and the data slot has shrink to only the ID
# summary(oa.sc)

@@

# build oa for GB
oa.gb <- spRbind(oa.ew, oa.sc)
rm(oa.ew, oa.sc)

# oa.gb$geometry <- oa.gb$geometry %>%
#   s2::s2_rebuild() %>%
#   sf::st_as_sfc()

# get GB
path.gb <- "/hdd/internet_archive/archive/gis/Countries_December_2014_Full_Clipped_Boundaries_in_Great_Britain.shp"
gb <- readOGR(path.gb)
# spatial transformations
gb <- spTransform(gb, CRS("+init=epsg:4326"))

## lisa maps

#path.out <- paste0(path, "/outputs/lisa_level_pc", n, "_oa") # for unique PC
path.out <- paste0(path, "/outputs/lisa_level_pc", m, "_oa")  # for multiple PC

morani <- data.frame()

#spatial weight matrix
sf_use_s2(FALSE)
nb <- poly2nb(oa.gb)
listw <- nb2listw(nb, style = "W", zero.policy = T)

for (t in 1996:2012){
test <- oa.gb
test@data <- test@data %>% left_join(df[df$year==t,], by = c("id"="oa11cd")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

#spatial weight matrix
#moved out of the loop

#Moran's I
globalMoran <- moran.test(test$n, listw, zero.policy = T, na.action = na.exclude)
a <- cbind(globalMoran$estimate[[1]],globalMoran$p.value, t[1])
morani <- rbind(a, morani)

#LISA
lmoran<- cbind(test@data, localmoran(test$n, listw,  adjust.x=TRUE, zero.policy = T, na.action = na.exclude))
#lmoran

# centers the local Moran's around the mean
lmoran$Ii <- lmoran$Ii - mean(lmoran$Ii, na.rm = TRUE) 
lmoran$lag.n<-  lag.listw(listw,lmoran$n, NAOK = TRUE)

# centers the variable of interest around its mean

lmoran$ns <- lmoran$n - mean(lmoran$n, na.rm = TRUE) 
lmoran$lag.n <- lmoran$lag.n - mean(lmoran$lag.n, na.rm = TRUE)

signif <- 0.05
#lmoran

lmoran <- lmoran%>% 
  mutate(quadrant= ifelse(ns>0 & lag.n > 0, 1, 0)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.n < 0, 2, quadrant)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.n > 0, 3, quadrant)) %>% 
  mutate(quadrant= ifelse(ns>0 & lag.n < 0, 4, quadrant)) %>%   
  #mutate(quadrant= ifelse(lmoran$`Pr(z > 0)` > signif, 0, quadrant)) #%>% 
  mutate(quadrant= ifelse(lmoran$`Pr(z != E(Ii))` > signif, 0, quadrant)) #%>%

#   mutate(quadrant2= ifelse(ANC_st>0 & lagANC_st > 0, 1, 0)) %>% 
# mutate(quadrant2= ifelse(ANC_st<0 & lagANC_st < 0, 2, quadrant2)) %>% 
#   mutate(quadrant2= ifelse(ANC_st<0 & lagANC_st > 0, 3, quadrant2)) %>% 
#  mutate(quadrant2= ifelse(ANC_st>0 & lagANC_st < 0, 4, quadrant2)) %>% 
#  mutate(quadrant2= ifelse(lmoran$LISA_PANC > signif, 0, quadrant2))

mun_merge_new<- merge(test, lmoran, by="id")

# R p value map
breaks = c(0, 1, 2, 3, 4, 5)

cities <- maps::world.cities %>% 
  filter(country.etc=="UK") %>% 
  arrange(pop) %>% tail(10) 
tif_sf <- st_as_sf(cities, coords = c("long", "lat"), crs = 4326)

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, OA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(gb, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}
```

Moran I

```{r}
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  kable()

## Gini

gini.df <- data.frame()

for (t in 1996:2012){
    a <- df %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}
```

## Getis-Ord

t= 1998
local_g <- localG(OA.Census$Qualification, nb_lw)
local_g <- localG(df[df$year==t,]$n, listw)

local_g <- cbind(OA.Census, as.matrix(local_g))
names(local_g)[6] <- "gstat"

@@

# NOT USED AS IT SCREWS UP THE REGRESSIONS
# Complete panel, N = 3871903, 17 year * 227759 OA
# df <- df %>% bind_rows(dist %>% select(oa11cd)) %>% 
#   mutate(year = ifelse(is.na(year),1000, year),
#          country = substring(oa11cd, 1, 1)) %>% 
#   filter(country != "L" & country != "M" & country != "N") %>% 
#   filter(!is.na(country)) %>% 
#   complete(year, oa11cd, fill = list(n = 0)) %>% 
#   filter(year!=1000,
#          !is.na(oa11cd)) %>% 
#   select(-country)

@@

# Join with distance and area
df <- df %>% left_join(dist, by = c("oa11cd" = "oa11cd")) %>% 
  left_join(oa.gb@data, by = c("oa11cd" = "id")) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)
sapply(df, function(x) sum(is.na(x)))
```

@@

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% select(oa11cd, dist.retail)

@@

sapply(df, function(x) sum(is.na(x)))
```

Website density regressions to London

```{r}
dens.London <- data.frame()
out.model <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(London), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.London <- rbind(r2, dens.London)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.model <- rbind(out.model_, out.model)
}

names(dens.London)[1] <- "rsquared"
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared))

library(broom)
out.model <- out.model %>% 
  mutate(year = 1996:2012)

ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() 
```

Website density regressions to the nearest city

```{r}
dens.distMet <- data.frame()
out.modelMet <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(dist), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.distMet <- rbind(r2, dens.distMet)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.modelMet <- rbind(out.model_, out.modelMet)
}

names(dens.distMet)[1] <- "rsquared"
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared))

out.modelMet <- out.modelMet %>% 
  mutate(year = 1996:2012)

ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() 
```

Website density regressions to the nearest retail centre

```{r}
dens.dist.retail <- data.frame()
out.model.retail <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(dist.retail+0.001), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.dist.retail <- rbind(r2, dens.dist.retail)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.model.retail <- rbind(out.model_, out.model.retail)
}

names(dens.dist.retail)[1] <- "rsquared"
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared))

out.model.retail <- out.model.retail %>% 
  mutate(year = 1996:2012)

ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip()

# library(pscl)
# m1 <- zeroinfl((n) ~ log(dist.retail+0.001),
#   data = df[df$year==t,], dist = "negbin", EM = TRUE)
# summary(m1)
# 
# df %>% filter(year == 1996) %>% 
#   group_by(group = cut(n, breaks = c(0, 1, 2, 10, 100, 1000, 10000), include.lowest = T, right = F)) %>%  #seq(0, max(n), 100))) %>%
#   summarise(n = sum(n))
```

Website density regressions to the nearest retail centre with spatial lag

```{r}
library(spatialreg)

model <- lagsarlm(log(density+0.1) ~ log(dist.retail+0.1), data = df[df$year==t,], 
                  listw, tol.solve = 1e-30, zero.policy = T)

dens.dist.retail <- data.frame()
for (t in 1996:2012){
  model <- lm(log(density) ~ log(dist.retail+0.1), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.dist.retail <- rbind(r2, dens.dist.retail)
}
names(dens.dist.retail)[1] <- "rsquared"
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared))

@@

## HH clusters

```{r}
hh <- mun_merge_new@data %>% filter(quadrant==1) %>% 
  select(id, quadrant) %>% 
  left_join(df[df$year==2000,], by =c("id" = "oa11cd")) %>% 
  select(id, year, n, area, density, London, dist, dist.retail)

hh.London <- lm(log(density+0.001) ~ log(London), data = hh)
summary(hh.London)
hh.dist <- lm(log(density+0.001) ~ log(dist), data = hh)
summary(hh.dist)
hh.retail <- lm(log(density+0.001) ~ log(dist.retail+0.001), data = hh)
summary(hh.retail)

data.folder <- "/hdd/internet_archive/archive/data/"
data.path9610 <- paste0(data.folder, "domain_pc_year.csv")
#Created by domain.R, which uses domain instead of host.
#This is what we use for the hyperlinks paper as per George's script

df9610 <- read_csv(data.path9610) %>% 
  filter(V1.domain == n,
         year == 1999) %>% 
  left_join(lookup, by = "pc", suffix =c("",""))

hh %>% left_join(df9610, by =c("id"="oa11cd"))

Spatial regression

```{r}
library(splm)
m <- spml(log(n)~lag(log(n)), data = df, listw = listw, lag = TRUE, spatial.error = "b", 
          model = "within", effect = "individual", method = "eigen", na.action = na.fail)

>>>>

---
title: "point.distance"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

library(tidyverse)
library(rprojroot)
library(rgdal)
library(spdep)
library(dbscan)

@@

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  select(pcds, oa11cd) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd

# path.lookup <- "/hdd/internet_archive/archive/ONSPD_FEB_2017_UK.csv"
# lookup <- read_csv(path.lookup) %>% 
#   select(pcds, oseast1m, osnrth1m) %>% 
#   dplyr::rename(pc = pcds)

The internet archive data is saved on /hdd.

```{r}
n = 1 #number of unique postcodes

data.folder9610 <- "/hdd/internet_archive/archive/data/"
data.path9610 <- paste0(data.folder9610, "domain_pc_year.csv")
#Created by domain.R, which uses domain instead of host.
#This is what we use for the hyperlinks paper as per George's script

data.path1112 <- paste0(path, "/data/temp/domain_pc_year1112.csv")
#Created by domain1112.Rmd, which is based on domain.R and uses domain instead of host.
#This is what we use for the hyperlinks paper as per George's script

df9610 <- read_csv(data.path9610) 
df1112 <- read_csv(data.path1112)

df <- bind_rows(df9610, df1112) %>% 
  filter(V1.domain == n,
         year > 1995) %>% 
  left_join(lookup, by = "pc", suffix =c("",""))

rm(df9610, df1112)
```

## Boundary data

```{r}
# get GB
path.gb <- paste0(path, "/data/raw/Countries_(December_2020)_UK_BUC.geojson")
gb <- readOGR(path.gb) 
# spatial transformations
gb <- spTransform(gb, CRS("+init=epsg:4326"))
gb <- subset(gb, CTRY20NM != "Northern Ireland")
gb.df <- fortify(gb, region = "CTRY20NM")

# cities
cities <- maps::world.cities %>% 
  filter(country.etc=="UK") %>% 
  arrange(pop) %>% tail(10) 
tif_sf <- st_as_sf(cities, coords = c("long", "lat"), crs = 4326)

# get OA for England and Wales
path.geo <- paste0(path, "/data/raw/Output_Areas__December_2011__Boundaries_EW_BGC.geojson")
oa.ew <- readOGR(path.geo)
# source: https://geoportal.statistics.gov.uk/

@@

@@

# build oa for GB
oa.gb <- spRbind(oa.ew, oa.sc)
rm(oa.ew, oa.sc)
```

@@

@@

# Join with distance and area
```

@@

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% select(oa11cd, dist.retail)
```

Joins

**IMPORTANT** these are distants not to points but to the centroids of the OA they fall within.

df <- df %>% left_join(dist, by = c("oa11cd" = "oa11cd")) %>% 
  left_join(oa.gb@data, by = c("oa11cd" = "id")) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)
sapply(df, function(x) sum(is.na(x)))

@@

sapply(df, function(x) sum(is.na(x)))

@@

## distance to London plot

```{r}
df %>%
  #mutate(text = fct_reorder(text, value)) %>%
  ggplot( aes(x=London, color=year, fill=year)) +
    geom_histogram(alpha=0.6, binwidth = 5) +
    #scale_fill_viridis(discrete=F) +
    #scale_color_viridis(discrete=F) +
    #theme_ipsum() +

  theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    ) +
    xlab("") +
    ylab("domains") +
    facet_wrap(~year, scales = "free_y")
```

## distance to cities plot

```{r}
df %>%
  #mutate(text = fct_reorder(text, value)) %>%
  ggplot( aes(x=dist, color=year, fill=year)) +
  geom_histogram(alpha=0.6, binwidth = 5) +
    #scale_fill_viridis(discrete=F) +
    #scale_color_viridis(discrete=F) +
    #theme_ipsum() +

  # geom_histogram(aes(y = stat(count) / sum(count)), alpha=0.6, binwidth = 5) +
  # scale_y_continuous(labels = scales::percent)+

  theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    ) +
    xlab("") +
    ylab("domains") +
    facet_wrap(~year, scales = "free_y")
```

## distance to retail centres

```{r}
df %>%
  #mutate(text = fct_reorder(text, value)) %>%
  ggplot( aes(x=dist.retail, color=year, fill=year)) +
    geom_histogram(alpha=0.6, binwidth = 5) +
    #scale_fill_viridis(discrete=F) +
    #scale_color_viridis(discrete=F) +
    #theme_ipsum() +

  theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    ) +
    xlab("") +
    ylab("domains") +
    facet_wrap(~year, scales = "free_y")
```
